\textbf{Computation and Neural Manifolds}

### 2025-04-19 Neural-Manifolds/neural-manifolds_v0.tex
adding cool images

@@

@@

@@

@@

>>>>

\centering
\begin{minipage}{1\textwidth}
    \centering
    \includegraphics[width=0.4\textwidth]{images/gallego_et_al-2017_01.PNG} % Replace with your image file
    \captionof{figure}{manifold}
\end{minipage}

Trajectory of time-varying population activity in the neural space of the three recorded neurons (black). The trajectory is mostly confined to the neural manifold, a plane shown in gray and spanned by the neural modes $u_1$ and $u_2$.

@@

\centering
\begin{minipage}{1\textwidth}
    \centering
    \includegraphics[width=0.4\textwidth]{images/Sohn_et_al-2019_01.PNG} % Replace with your image file
    \captionof{figure}{temporal interval estimation}
\end{minipage}

Schematic of a single trial of the ReadySet-Go task. The animal has to estimate a sample interval, ts, between Ready and Set (estimation epoch), and produce a matching interval, tp, after Set with a delayed response (Go) via a saccade or a movement of the joystick (production epoch).

@@

\centering
\begin{minipage}{1\textwidth}
    \centering
    \includegraphics[width=0.4\textwidth]{images/Sohn_et_al-2019_02.PNG} % Replace with your image file
    \captionof{figure}{temporal interval estimation}
\end{minipage}

@@

\centering
\begin{minipage}{1\textwidth}
    \centering
    \includegraphics[width=0.4\textwidth]{images/Sohn_et_al-2019_03.PNG} % Replace with your image file
    \captionof{figure}{temporal interval estimation}
\end{minipage}

% Behavior. Top: a representative session for monkey H showing tp pooled across effectors and target directions (small dots, individual trials; large open circles, average tp per ts; solid lines, Bayesian model; diagonal, unity line). The horizontal location of dots was jittered to facilitate visualization. Right: histograms of tp for the overlapping ts (horizontal dashed line) for the two prior conditions (orange, Short; blue, Long; triangles, averages). Top-left inset: average error (i.e., bias) for each ts (circles, data; solid lines, Bayesian model). Bottom-right inset: histogram of regression slopes relating tp to ts across sessions (red, Short; blue, Long; triangles, averages). Bottom: the same as top for monkey G.

@@

\centering
\begin{minipage}{1\textwidth}
    \centering
    \includegraphics[width=0.4\textwidth]{images/Sohn_et_al-2019_04.PNG} % Replace with your image file
    \captionof{figure}{temporal interval estimation}
\end{minipage}
